Python as a machine learning language: experiences from the scikit-learn project

### 2013-06-12 paper.tex
api principles

\begin{description}
  \item[Consistency.]
       All objects (basic or composed) share a consistent interface composed of
       a limited set of methods.
  \item[Inspection.]
       Constructor parameters and parameter values determined by learning
       algorithms are stored as public attributes. All of them are documented in
       a consistent manner.
       % Gilles: Do we really need to bother the reader with such details?
       % (The Python language does not actually distinguish
       % between public and private attributes of objects,
       % but by convention, any identifier
       % prefixed with an underscore (\texttt{\_})
       % is considered ``a non-public part of the API''; \citealp{pythontut}.)
  \item[Non-proliferation of classes.]
       Only learning algorithms are objects of custom classes.
       Datasets and hyperparameter names and values
       are represented as standard Python, NumPy or SciPy classes
       rather than new ones whenever feasible.
       % Gilles: I don't understand the phrase below
       % Custom classes adhere to Python conventions and protocols
       % for constructs such as iteration over the folds
       % in a $k$-fold cross validation.
       This should keep \sklearn easy to use
       and easy to combine with other libraries.
       % XXX do we need to elaborate more on this, or do we expect everyone
       % to be an experienced Java/adapter pattern hater?
  % Gilles: this is actually not a design principle
  % \item[Composition.]
  %      Many machine learning tasks are expressible
  %      as sequences or combinations of transformations to data.
  %      Some learning algorithms are also naturally viewed
  %      as meta-algorithms parameterized on other algorithms.
  %      To be able to implement and use these algorithms in a simple way,
  %      % Gilles: let elaborate later on the syntax
  %      % and a simple syntax is implemented
  %      % for setting and retrieving parameters of sub-estimators.
  %      % XXX need to describe this!
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       a default and appropriate value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}

>>>>

\begin{description}
  \item[Consistency.]
       All objects (basic or composed) share a consistent interface composed of
       a limited set of methods. This interface is documented in a consistent
       manner for all objects.
  \item[Inspection.]
       Constructor parameters and parameter values determined by learning
       algorithms are stored and exposed as public attributes.
  \item[Non-proliferation of classes.]
       Learning algorithms are the only objects to be of custom classes.
       Datasets and hyperparameter names and values are represented as standard
       Python, NumPy or SciPy classes rather than new ones whenever feasible.
       This keeps \sklearn easy to use and easy to combine with other libraries.
       % XXX do we need to elaborate more on this, or do we expect everyone
       % to be an experienced Java/adapter pattern hater?
  % Gilles: this is actually not a design principle
  \item[Composition.]
       Many machine learning tasks are expressible
       as sequences or combinations of transformations to data.
       Some learning algorithms are also naturally viewed
       as meta-algorithms parameterized on other algorithms.
       Whenever possible, those algorithms are composed from
       existing building blocks.
       % Gilles: let elaborate later on the syntax
       % and a simple syntax is implemented
       % for setting and retrieving parameters of sub-estimators.
       % XXX need to describe this!
  \item[Sensible defaults.]
       Whenever an operation requires a user-defined parameter,
       a default and appropriate value is defined by the library.
       The default value should cause the operation to be performed
       in a sensible way (giving a baseline solution for the task at hand).
\end{description}
